### 2011-06-15 docs/runtime_parameters/runtime_parameters.tex
add change_max_grdi_size_1 to parameters table
update doc

@@

@@

\verb=  dump_grid_file  = &    &  .false. \\

@@

@@

@@

>>>>

\verb=  change_max_grid_size_1  = &   Change the max grid size on the base level on restart  &  .false. \\

@@

\verb=  do_heating  = &   use analytic heating  &  .false. \\

@@

\verb=  dump_grid_file  = &   dump out a file, named grids.out, containing the number of grids a each level.  A new line is added each time regrid is called.  &  .false. \\

@@

\verb=  sdc_iters  = &   how many SDC iteractions to take (requires the code be compiled with {\tt SDC := t}  &  4 \\

@@

\verb=  species_pred_type  = &   Which quantities do we predict to the edges for computing the ($\rho X$) edge states?  \newline {\tt species\_pred\_type} = 1 means predict $\rho^\prime$ and $X$ separately.  \newline {\tt species\_pred\_type} = 2 means predict the full ($\rho X$) itself. \newline {\tt species\_pred\_type} = 3 means predict $\rho$ and $X$ separately.  &  1 \\

@@

\verb=  use_linear_grav_in_beta  = &   how to represent gravity in the beta0 integration: .true. = piecewise linear .false. = piecewise constant  &  .false. \\
\verb=  use_particles  = &   call the particle initialization, advection, etc. routines.  &  .false. \\
